Reproducible Research Project 1
=====================

# Loading and Preprossing the data
```{r load data}
    setwd('C:/Analytics/Coursera Training/5- Reproducible Research/Week 2/Project')
    data<-read.csv('C:/Analytics/Coursera Training/5- Reproducible Research/Week 2/Project/activity.csv')
    knitr::opts_chunk$set(echo = TRUE)
```

# What is mean total number of steps taken per day?
```{r plot 1}
library(ggplot2)
totalsteps <- tapply(data$steps, data$date, FUN=sum, na.rm=TRUE)
qplot(totalsteps, xlab="total number of steps taken per day")
mean(totalsteps, na.rm=TRUE)
median(totalsteps, na.rm=TRUE)
```

#What is the average daily activity pattern?
```{r plot 2}
library(ggplot2)
average.activity <- aggregate(x=list(steps=data$steps), by=list(interval=data$interval),
                      FUN=mean, na.rm=TRUE)
ggplot(data=average.activity, aes(x=interval, y=steps)) +
    geom_line() +
    xlab("5-minute interval") +
    ylab("average number of steps taken")

average.activity[which.max(average.activity$steps),]
```

#Imputing missing values
## First Compute how many missing data
```{r plot 3.1}
missing <- is.na(data$steps)
table(missing)
```
## Second Replace each missing value with the mean value within its 5-minute interval
```{r plot 3.2}
fill.value <- function(steps, interval) {
    filled <- NA
    if (!is.na(steps))
        filled <- c(steps)
    else
        filled <- (average.activity[average.activity$interval==interval, "steps"])
    return(filled)
}
filled.data <- data
filled.data$steps <- mapply(fill.value, filled.data$steps, filled.data$interval)
```

##Finally generate plots of total number of steps taken each day
```{r plot 3.3}
totalsteps <- tapply(filled.data$steps, filled.data$date, FUN=sum)
qplot(totalsteps, xlab="total number of steps taken each day")
mean(totalsteps)
median(totalsteps)
```
## The mean and median are larger than the above results when null values are not being replaced with the mean within its 5-minute interval.

#Are there differences in activity patterns between weekdays and weekends?
## Fist differentiate weekday from weekend
```{r plot 4.1}
weekday.weekend <- function(date) {
    day <- weekdays(date)
    if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
        return("weekday")
    else if (day %in% c("Saturday", "Sunday"))
        return("weekend")
    else
        stop("invalid date")
}
filled.data$date <- as.Date(filled.data$date)
filled.data$day <- sapply(filled.data$date, FUN=weekday.weekend)
```
## Second generate the plot of the number of steps during weekdays and weekends respectively
```{r plot 4.2}
average <- aggregate(steps ~ interval + day, data=filled.data, mean)
ggplot(average, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) +
    xlab("5-minute interval") + ylab("Number of steps")
```
## Weekends tend to show more activities than weekday